\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{url}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\begin{center}
    \textbf{Works Cited}
\end{center}

\vspace{1em}

\begin{enumerate}[label={[\arabic*]}, leftmargin=*, itemsep=1em]

\item Bardou, A., et al. ``Improving the Spatial Reuse in IEEE 802.11ax WLANs: A Multi-Armed Bandit Approach.'' \textit{Proceedings of the 24th ACM International Conference on Modeling, Analysis and Simulation of Wireless and Mobile Systems (MSWiM '21)}, ACM, 2021, pp. 135–144.

\item Bellalta, Boris. ``IEEE 802.11ax: High-Efficiency WLANs.'' \textit{IEEE Wireless Communications}, vol. 23, no. 1, 2016, pp. 38–46.

\item Bianchi, Giuseppe. ``Performance Analysis of the IEEE 802.11 Distributed Coordination Function.'' \textit{IEEE Journal on Selected Areas in Communications}, vol. 18, no. 3, 2000, pp. 535–547.

\item Dogan-Tusha, B., et al. ``Evaluating the Interference Potential in 6 GHz: An Extensive Measurement Campaign of a Dense Indoor Wi-Fi 6E Network.'' \textit{Proceedings of the 2023 ACM MobiCom Workshop on Wireless Network Testbeds, Experimental evaluation \& Characterization (WiNTECH '23)}, ACM, 2023, pp. 56–63.

\item Garcia-Rodriguez, A., et al. ``IEEE 802.11be: Wi-Fi 7 Strikes Back.'' \textit{IEEE Communications Magazine}, vol. 59, no. 4, 2021, pp. 102–108.

\item IEEE. \textit{IEEE Std 802.11ax-2021: IEEE Standard for Information Technology – Telecommunications and Information Exchange Between Systems – Local and Metropolitan Area Networks – Specific Requirements – Part 11: Wireless LAN Medium Access Control (MAC) and Physical Layer (PHY) Specifications – Amendment 1: Enhancements for High Efficiency WLAN}. IEEE, 2021.

\item Jin, Y., et al. ``Design and Evaluation of IEEE 802.11ax Uplink Orthogonal Multiple Access.'' \textit{Proceedings of the 2025 IEEE Wireless Communications and Networking Conference (WCNC)}, IEEE, 2025.

\item Kaufman, J.S. ``Blocking in a Shared Resource Environment.'' \textit{IEEE Transactions on Communications}, vol. 29, no. 10, 1981, pp. 1474–1481.

\item Knitter, M., and R. Kays. ``Spatial Reuse Insights for IEEE 802.11ax and IEEE 802.11be WLANs and Beyond.'' \textit{Proceedings of the 2022 IEEE 33rd Annual International Symposium on Personal, Indoor and Mobile Radio Communications (PIMRC)}, IEEE, 2022, pp. 919–925.

\item Lanante, L., and S. Roy. ``Performance Analysis of the IEEE 802.11ax OBSS\_PD-Based Spatial Reuse.'' \textit{IEEE/ACM Transactions on Networking}, vol. 30, no. 2, 2022, pp. 616–628.

\item Liu, Y., et al. ``Performance Optimization of IEEE 802.11ax UL OFDMA Random Access.'' \textit{Journal of Communications and Networks}, vol. 26, no. 6, 2024, pp. 580–592.

\item MediaTek. ``Wi-Fi 6/6E: Anti-Interference Technologies.'' \textit{MediaTek White Paper}, 2025, https://www.mediatek.com/. Accessed 22 Nov. 2025.

\item Mozaffariahrar, E., et al. ``A Survey of Wi-Fi 6: Technologies, Advances, and Challenges.'' \textit{Future Internet}, vol. 14, no. 10, 2022, art. 293.

\item ns-3 Consortium. ``The ns-3 Network Simulator.'' \textit{nsnam.org}, https://www.nsnam.org/. Accessed 22 Nov. 2025.

\item Rehman, A., et al. ``Enhancing Wi-Fi 6 Spectrum Access Control with a Heuristic OFDMA Back-off Mechanism.'' \textit{Results in Engineering}, vol. 26, 2025, art. 105086.

\item Smith, J., et al. ``Feedback-Based Congestion Control for Airtime Fairness in Wireless Networks.'' \textit{Wireless Networks}, Springer, 2025. (In Press).

\item Wilhelmi, Francesc, et al. ``Spatial Reuse in IEEE 802.11ax WLANs.'' \textit{Computer Communications}, vol. 170, 2021, pp. 65–83.

\item Zhang, Y., et al. ``DDPG-based Multi-AP Cooperative Access Control in Dense Wi-Fi Networks.'' \textit{Proceedings of IEEE VTC-Fall 2023}, IEEE, 2023, pp. 1–6.

\item ZTE Corporation. ``Wi-Fi Multi-AP Home Network Technology White Paper.'' \textit{ZTE Technologies}, 2024, https://www.zte.com.cn/. Accessed 22 Nov. 2025.

\end{enumerate}

\end{document}
